---
title: "Credit Card Fraud NN"
output: html_notebook
---

***NOTE: creditcard.csv file too large to store on gitub. Link to file download is here: https://drive.google.com/file/d/1PGXzrbvw0n-fNGYPfgYDxsOmCrLErcIK/view?usp=sharing ***

Purpose of this R notebook is to detect credit card fraud via supervised learning ANN algo.

```{r}
library(MASS)
```

Load Keras

```{r}
install.packages("devtools")
devtools::install_github("rstudio/keras") # update all if prompted
library(keras)
install_keras() # install Miniconda if prompted
```

Import credit card CSV. 

```{r}
card_data <- read.csv("creditcard.csv")
```

```{r}
head(card_data)
names(card_data)
```

Scale data to deal with outliers.

```{r}
card_data$Amount=scale(card_data$Amount)
scaled_card_data = card_data[,-c(1)]
head(scaled_card_data)
```

Split data into training & test (80/20)

```{r}
set.seed(2020)
sample_ind <- sample(1:nrow(scaled_card_data), size=round(0.8*nrow(scaled_card_data)), replace=FALSE)
train_card_x = as.matrix(scaled_card_data[sample_ind,-30])
test_card_x = as.matrix(scaled_card_data[-sample_ind,-30])
train_card_y  = model.matrix(~Class-1, data=scaled_card_data[sample_ind,])
test_card_y = model.matrix(~Class-1, data=scaled_card_data[-sample_ind,])
head(train_card_x)
head(train_card_y)
```

Check dimensions
```{r}
dim(train_card_x)
dim(test_card_x)
```

Train FNN with one hidden layer wit relu activation, and a softmax output rule.

```{r}
hidden_layer <- layer_dense(units = 50, activation = "relu", input_shape = dim(train_card_x)[2])
hidden_layer_2 <- layer_dense(units = 25, activation = "relu", input_shape = 50)
output_layer <- layer_dense(units = 2, activation = "softmax")
model <- keras_model_sequential(list(hidden_layer, hidden_layer_2, output_layer))
summary(model)
```

Now, we specify model by setting loss function to negative log-lik, train the model using mini-batch SGD and evaluate model to get predictions (after running several times, found almost all data to be captured in 4 epochs).

```{r}
compile(model, optimizer="sgd", loss="sparse_categorical_crossentropy", metrics="acc")
fit(model, train_card_x, train_card_y, epochs=4, batch_size=10)
evaluate(model, test_card_x, test_card_y)
```








